---
title: "Caleb's Permit Analysis"
output: html_notebook
---

To begin our analysis, let's first install our libraries.

```{r}
library(tidyverse) #To conduct our analysis
library(janitor) #clean the data
library(lubridate) #To clean and rearrange dates
```

Next, let's store and clean the data.

```{r}
Permit_data <- read_csv("data/PG_permit_data.csv") |> clean_names() |> mutate(across(zip_code, as.character))
```

Now, let's analyze the zip codes. When we count how many times each zip ccode appears, it will tell us how many permits were registered and where.

```{r}
Permit_data |> group_by(zip_code) |> summarise(count=n()) |> arrange(desc(count))
```

Since 2013 through 2022, there have been a total of 7,711 registered permits across these four zip codes.

But this is interesting! Across 9 years, only a single permit was registered in the 20704 zip code. Let's find out more.

Here is the case.

```{r}
Permit_data |> filter(str_detect(zip_code,"20704"))
```

Colonial Electric Company INC registered for a building permit in 2019. The permit goes into effect on October 17, 2019.

The address, 4709 AMHERST COLLEGE PARK,MD 20704, is to a small family house six minutes away from campus.

Let's see if the company has other permits involving buildings near campus.

```{r}
Permit_data |> filter(str_detect(case_name, "COLONIAL ELECTRIC COMPANY INC"))
```
The company only has one other listing. Its another building permit for a small family house near campus.

Not super exciting, but it shows a trend. Look at this:

```{r}
Permit_data |> filter(str_detect(case_name, "electric"))
Permit_data |> filter(str_detect(case_name, "Electric"))
Permit_data |> filter(str_detect(case_name, "ELECTRIC"))
```

The first electric company helped us find all of these other electric companies with building permits for nearby houses in College Park.

My journalistic hypothesis is that these electric companies could be competing with one another in the student housing market.