---
title: Caleb's Data Analysis
output: html_notebook
---

First, let's load our libraries

```{r}
library(tidyverse)
library(janitor)
library(lubridate)
```

Next, let's load our data set and clean it up

```{r}
Student_Responses <- read.csv("data/student_responses.csv") |> clean_names()
```

Now, time to analyze.

1Q. Which news organizations are student listening to the most this past month?

```{r}
Student_Responses |> 
  group_by(most_frequent_news_organization) |> 
  summarise(count=n()) |>
  arrange(desc(count))
```

A1. Most of the students in this sample have been reading the New York Times the more frequently last month than any other news organization.

During the month of April, many big political events occurred. New York Times is know for covering a wide range of political matters.

2Q. Which race/ethnicity of students most frequently read the Times this past month?

```{r}
Student_Responses |>
  filter(str_detect(most_frequent_news_organization, "New York Times")) |>
  group_by(race_ethnicity) |>
  summarise(count=n()) |>
  arrange(desc(count))
```

A2. In the sample, white journalism student have read the Times the most.

Q3. For those reading the Times, how frequent have they been reading?

```{r}
Student_Responses |> filter(str_detect(most_frequent_news_organization, "New York Times")) |> group_by(how_frequent) |> summarise(count=n()) |> arrange(desc(count))
```

A3. During last month, 6 students read the New York Times everyday. 3 students read the Times 6 - 8 times a week. Only 1 student read the Times once a week.

Q4. What were these students' reasons for sticking with the Times? Do any of them share reasons?

```{r}
Why_1 <- Student_Responses |> filter(str_detect(most_frequent_news_organization, "New York Times"))
```

A4. Most students wanted to learn about recent events. The second most popular reason was that the students trusted the Times with ethical reporting. The third most popular reasons was that the students enjoyed the expertise from the Times.

Q5. The New York Times is these students' most frequently read new organization. But what did they say was their favorite news organization. How long do these spent reading it weekly?

```{r}
NYT_most_frequent |> select(name,favorite_news_organization, how_much)
```

A5. Only two students reported the New York Times as their favorite. Other students reported other news organizations as their favorite such as the AP, Baltimore Banner, Washington Post, Vox, ect.

Rachel Lawrence reads her favorite news orgaization, the Associated Press, 6 - 8 a week.

Theodore Rose reads his favorite news organization, Bellingcat, 2 - 4 times a week.
