---
title: "Caleb's Comic Book Data Project"
output: html_notebook
---

Before anything, let's load are libraries. We'll need three:
```{r}
library(tidyverse)
library(lubridate)
library(janitor)
```

Both data sets from the article can be found below. Go ahead and click play to receive them.

```{r}
Marvel_data <- read.csv("data/marvel-wikia-data.csv")
DC_data <- read.csv("data/dc-wikia-data.csv")
```

Now, let's clean the data sets, making them easier to read.

```{r}
Marvel_data <- Marvel_data |> clean_names()
DC_data <- DC_data |> clean_names()
```

Now that they're both cleaned up, let's take a glimpse at both datasets.

```{r}
glimpse(Marvel_data)
glimpse(DC_data)
```


Q1: How many charterers does Marvel Comics have? How many does DC Comics have? Find the number of women characters that each company has.
```{r}
Marvel_data |> group_by(name) |> summarise(count = n(), total = sum(count))
DC_data |> group_by(name) |> summarise(count = n(), total = sum(count))

Marvel_data |> group_by(sex) |> summarise(count = n(), total = sum(count)) |> arrange(desc(count))
DC_data |> group_by(sex) |> summarise(count = n(), total = sum(count)) |> arrange(desc(count))
```
A1: Marvel Comics has 16,376 characters in total while DC Comics has 6,896 characters. Marvel Comics has a total of 3,837 female characters while DC Comics has a total of 1967 female characters.

Great! This is a lot of characters! And through our data analysis, we can see that women are extremely underrepresented in the comic medium. Now, let's show our findings as percentages.

Q2: Find the percentage between Marvel Comics' male characters and female characters. Then do the same for DC Comics' male and female characters.

First, let's make four places to store our values:
```{r}
M_males <- 11638
M_females <- 3837
M_total_char <- 16376
DC_males <- 4783
DC_females <-1967
DC_total_char <- 6896
```

Then, let's do the math:

```{r}
M_pct_men = (M_males/M_total_char)*100
M_pct_females = (M_females/M_total_char)*100
DC_pct_men = (DC_males/DC_total_char)*100
DC_pct_female = (DC_females/DC_total_char)*100
```

A2: In percentages, Marvel Comics has 71% male characters and 23% female characters. DC Comics has 69% males and 28% females.

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
