---
title: "Caleb's Comic Book Data Project"
output: html_notebook
---

Before anything, let's load are libraries. We'll need three:

```{r}
library(tidyverse)
library(lubridate)
library(janitor)
```

Both data sets from the article can be found below. Go ahead and click play to receive them.

```{r}
Marvel_data <- read.csv("data/marvel-wikia-data.csv")
DC_data <- read.csv("data/dc-wikia-data.csv")
```

Now, let's clean the data sets, making them easier to read.

```{r}
Marvel_data <- Marvel_data |> clean_names()
DC_data <- DC_data |> clean_names()
```

Now that they're both cleaned up, let's take a glimpse at both data sets.

```{r}
glimpse(Marvel_data)
glimpse(DC_data)
```

Q1: How many charterers does Marvel Comics have? How many does DC Comics have? Find the number of women characters that each company has.

```{r}
Marvel_data |> group_by(name) |> summarise(count = n(), total = sum(count))
DC_data |> group_by(name) |> summarise(count = n(), total = sum(count))

Marvel_data |> group_by(sex) |> summarise(count = n(), total = sum(count)) |> arrange(desc(count))
DC_data |> group_by(sex) |> summarise(count = n(), total = sum(count)) |> arrange(desc(count))
```

A1: Marvel Comics has 16,376 characters in total while DC Comics has 6,896 characters. Marvel Comics has a total of 3,837 female characters while DC Comics has a total of 1967 female characters.

Great! This is a lot of characters! And through our data analysis, we can see that women are extremely underrepresented in the comic medium. Now, let's show our findings as percentages.

Q2: Find the percentage between Marvel Comics' male characters and female characters. Then do the same for DC Comics' male and female characters.

First, let's make four places to store our values:

```{r}
M_males <- 11638
M_females <- 3837
M_total_char <- 16376
DC_males <- 4783
DC_females <-1967
DC_total_char <- 6896
```

Then, let's do the math:

```{r}
M_pct_men = (M_males/M_total_char)*100 
M_pct_females = (M_females/M_total_char)*100 
DC_pct_men = (DC_males/DC_total_char)*100
DC_pct_female = (DC_females/DC_total_char)*100
```

A2: In percentages, Marvel Comics has 71% male characters and 23% female characters. DC Comics has 69% males and 28% females.

Q3. Let's find out how many female characters are hero compared to villains.

```{r}
Marvel_feamle_heroes <- Marvel_data |> filter(sex == "Female Characters" & align == "Good Characters")
Marvel_feamle_villians <- Marvel_data |> filter(sex == "Female Characters" & align == "Bad Characters")
DC_feamle_heroes <- DC_data |> filter(sex == "Female Characters" & align == "Good Characters")
DC_female_villians <- DC_data |> filter(sex == "Female Characters" & align == "Bad Characters")
```

A3. Marvel Comics has 1,537 characters who are female heroes or listed a "Good Characters." Marvel Comics has only 976 evil or "Bad Characters" who are female. DC Comics has 935 "Good Characters" that are female and 597 female "Bad Characters."

Q4. In what year does the most female comic book characters first appear?

```{r}
Marvel_data |> filter(sex=="Female Characters") |> group_by(first_appearance) |> summarise(count=n()) |> arrange(desc(count))
DC_data |> filter(sex=="Female Characters") |> group_by(first_appearance) |> summarise(count=n()) |> arrange(desc(count))
```

A4: Both in September 2006 and August 2010 Marvel Comics introduced their most female characters: 23. DC Comics introduced their most female characters in September 1996: 18.

Q5: And just for the fun of it --- which hair color is the most common among female comic book characters?

```{r}
Marvel_data |> filter(sex == "Female Characters") |> group_by(hair) |> summarise(count=n()) |> arrange(desc(count))
```

A5 Pt1: 1048 female characters have black Hair - the most common hair color for female characters in Marvel Comics. Gold hair is the rarest hair color. Only one female character has it: Blitziana.

```{r}
Marvel_data |> filter(sex == "Female Characters") |> filter(hair=="Gold Hair")
```

For DC Comics:

```{r}
DC_data |> filter(sex == "Female Characters") |> group_by(hair) |> summarise(count=n()) |> arrange(desc(count))
```

Black hair is also the most common hair color among female characters: 509. Reddish Brown Hair is the rarest with only one person having it:

```{r}
DC_data |> filter(sex == "Female Characters") |> filter(hair=="Reddish Brown Hair")
```

Yolanda Montez.

These are my findings! I hope you enjoyed!
