---
title: "Caleb's Comic Book Data Project"
output: html_notebook
---

Both data sets from the article can be found below. Go ahead and click play to receive them.

```{r}
Marvel_data <- read.csv("data/marvel-wikia-data.csv")
DC_data <- read.csv("data/dc-wikia-data.csv")
```

Now, let's clean the data sets, making them easier to read.

```{r}
Marvel_data <- Marvel_data |> clean_names()
DC_data <- DC_data |> clean_names()
```


Q1: How many charterers does Marvel Comics have? How many does DC Comics have? Find the number of women charterers that each company has.


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
