---
title: "Caleb's Comic Book Data Project"
output: html_notebook
---

Before anything, let's load are libraries. We'll need three:
```{r}
library(tidyverse)
library(lubridate)
library(janitor)
```

Both data sets from the article can be found below. Go ahead and click play to receive them.

```{r}
Marvel_data <- read.csv("data/marvel-wikia-data.csv")
DC_data <- read.csv("data/dc-wikia-data.csv")
```

Now, let's clean the data sets, making them easier to read.

```{r}
Marvel_data <- Marvel_data |> clean_names()
DC_data <- DC_data |> clean_names()
```

Now that they're both cleaned up, let's take a glimpse at both datasets.

```{r}
glimpse(Marvel_data)
glimpse(DC_data)
```


Q1: How many charterers does Marvel Comics have? How many does DC Comics have? Find the number of women characters that each company has.
Here:
```{r}
Marvel_data |> group_by(name) |> summarise(count = n(), total = sum(count))
DC_data |> group_by(name) |> summarise(count = n(), total = sum(count))

Marvel_data |> group_by(sex) |> summarise(count = n(), total = sum(count)) |> arrange(desc(count))
DC_data |> group_by(sex) |> summarise(count = n(), total = sum(count)) |> arrange(desc(count))
```
A1: Marvel Comics has 16,376 characters in total while DC Comics has 6,896 characters. Marvel Comics has a total of 3,837 female characters while DC Comics has a total of 1967 female characters.


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
